Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-30 paper/paper.tex
Minor cosmetic changes.

% Maths operators
\newcommand{\nds}{\operatorname{nds}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }

@@

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\deg(p) - k \le \deg(t)$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
\]
\end{proof}

\begin{proposition}
    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
    $(\nds(p)[k+1] - k, \nds(p)[k+2] - k, \ldots) \preceq \nds(t)$.
\end{proposition}

@@

\todo{Define paths}

\begin{proposition}
    If $p \prescript{}{k}{\mapsto} t$ and $q \prescript{}{k}{\mapsto} u$ then
     $\operatorname{paths}(p, q, 2) \le \operatorname{paths}(t, u, 2) + k$.
\end{proposition}

>>>>

% Maths operators
\newcommand{\nds}{\operatorname{nds}}
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }

@@

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \lessmap t$ then
    $\deg(p) - k \le \deg(t)$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
\]
\end{proof}

\begin{proposition}
    More powerfully, if $p \lessmap t$ then
    $(\nds(p)[k+1] - k, \nds(p)[k+2] - k, \ldots) \preceq \nds(t)$.
\end{proposition}

@@

A \emph{path} between two vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$. We define $\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
%\todo{Define paths}

\begin{proposition}
    Let $p,q \in V(P)$ and $t,u\in V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) \le \paths(t, u, 2) + k$.
\end{proposition}
